Relación entre la legibilidad de libros y sus respectivas calificaciones

### 2017-02-02 Trabajo Final/paper/paper.tex
arreglo

\begin{minipage}{\linewidth}
  \centering
  \begin{minipage}{0.25\linewidth}
      \begin{figure}[H]
          \includegraphics[width=2.3in]{../unigrams/scripts/boxplots/not-normalized-ARI.png}
          \caption{ARI}
      \end{figure}
  \end{minipage}
  \hspace{0.05\linewidth}
  \begin{minipage}{0.25\linewidth}
      \begin{figure}[H]
          \includegraphics[width=2.3in]{../unigrams/scripts/boxplots/not-normalized-Coleman-Liau.png}
          \caption{Coleman-Liau}
      \end{figure}
  \end{minipage}
  \hspace{0.05\linewidth}
  \begin{minipage}{0.25\linewidth}
      \begin{figure}[H]
          \includegraphics[width=2.3in]{../unigrams/scripts/boxplots/not-normalized-SMOGIndex.png}
          \caption{SMOGIndex}
      \end{figure}
  \end{minipage}
\end{minipage}

\begin{minipage}{\linewidth}
  \centering
  \begin{minipage}{0.25\linewidth}
      \begin{figure}[H]
          \includegraphics[width=2.3in]{../unigrams/scripts/boxplots/not-normalized-FleschReadingEase.png}
          \caption{FleschReadingEase}
      \end{figure}
  \end{minipage}
  \hspace{0.05\linewidth}
  \begin{minipage}{0.25\linewidth}
      \begin{figure}[H]
          \includegraphics[width=2.3in]{../unigrams/scripts/boxplots/not-normalized-LIX.png}
          \caption{LIX}
      \end{figure}
  \end{minipage}
  \hspace{0.05\linewidth}
  \begin{minipage}{0.25\linewidth}
      \begin{figure}[H]
          \includegraphics[width=2.3in]{../unigrams/scripts/boxplots/not-normalized-Dale-Chall.png}
          \caption{Dale-Chall}
      \end{figure}
  \end{minipage}
\end{minipage}

>>>>

\begin{minipage}{\linewidth}
  \centering
  \begin{minipage}{0.25\linewidth}
      \begin{figure}[H]
          \includegraphics[width=2.3in]{../unigrams/scripts/boxplots/ARI.png}
          \caption{ARI}
      \end{figure}
  \end{minipage}
  \hspace{0.05\linewidth}
  \begin{minipage}{0.25\linewidth}
      \begin{figure}[H]
          \includegraphics[width=2.3in]{../unigrams/scripts/boxplots/Coleman-Liau.png}
          \caption{Coleman-Liau}
      \end{figure}
  \end{minipage}
  \hspace{0.05\linewidth}
  \begin{minipage}{0.25\linewidth}
      \begin{figure}[H]
          \includegraphics[width=2.3in]{../unigrams/scripts/boxplots/SMOGIndex.png}
          \caption{SMOGIndex}
      \end{figure}
  \end{minipage}
\end{minipage}

\begin{minipage}{\linewidth}
  \centering
  \begin{minipage}{0.25\linewidth}
      \begin{figure}[H]
          \includegraphics[width=2.3in]{../unigrams/scripts/boxplots/FleschReadingEase.png}
          \caption{Flesch}
      \end{figure}
  \end{minipage}
  \hspace{0.05\linewidth}
  \begin{minipage}{0.25\linewidth}
      \begin{figure}[H]
          \includegraphics[width=2.3in]{../unigrams/scripts/boxplots/LIX.png}
          \caption{LIX}
      \end{figure}
  \end{minipage}
  \hspace{0.05\linewidth}
  \begin{minipage}{0.25\linewidth}
      \begin{figure}[H]
          \includegraphics[width=2.3in]{../unigrams/scripts/boxplots/Dale-Chall.png}
          \caption{Dale-Chall}
      \end{figure}
  \end{minipage}
\end{minipage}
